Supermartingales and Termination Analysis of Statistical PCF

### 2020-12-31 LICS21/ranking.tex
Geometric distribution example: Adding another graph of reachable terms using fixpoint operator (instead of Y-combinator).

\lo{The graph can be simplified if we redefine general recursion using a fixpoint operator as per \Cref{eq:letrec redex}.
But (especially in view of the vast investment in the confluent trace semantics) it is perhaps too late to change things now?}

@@

    \draw [->] (1.south west) to [bend right=45] (2.north west);
    \draw [->] (2.south west) to [bend right=45] (3.north west);
    \draw [->] (3.south west) to [bend right=45] (4.north west);
    \draw [->] (4.south west) to [bend right=45] (5.north west);
    \draw [->] (5.south west) to [bend right=45] (6.north west);
    \draw [->] (6.south west) to [bend right=45] (8.north west);
    \draw [->] (8.south west) to [bend right=45] (9.north west);
    \draw [->] (9.south west) to [bend right=45] (10.north west);
    \draw [->] (6) to (7);
\end{tikzpicture}
\caption{Some reachable terms of $\tY \, \Theta \, \underline 0$\label{fig:geometric distribution 1}}
\end{figure}
\end{example}

>>>>

\lo{The graph can be simplified somewhat if we redefine general recursion using a fixpoint operator $\tY_{f, n}\Theta$ with redex rule as per \Cref{eq:letrec redex}: see \Cref{fig:geometric distribution 2}.
But (especially in view of the vast investment in the confluent trace semantics) it is perhaps too late to change things now?}

@@

    \draw [->] (1.south west) to [bend right=45] (2.north west);
    \draw [->] (2.south west) to [bend right=45] (3.north west);
    \draw [->] (3.south west) to [bend right=45] (4.north west);
    \draw [->] (4.south west) to [bend right=45] (5.north west);
    \draw [->] (5.south west) to [bend right=45] (6.north west);
    \draw [->] (6.south west) to [bend right=45] (8.north west);
    \draw [->] (8.south west) to [bend right=45] (9.north west);
    \draw [->] (9.south west) to [bend right=45] (10.north west);
    \draw [->] (6) to (7);
\end{tikzpicture}
\caption{Some reachable terms of $\tY \, \Theta \, \underline 0$\label{fig:geometric distribution 1}}
\end{figure}

\begin{figure}
\centering
\begin{tikzpicture}[node distance=0.5em, anchor=west]
    \node (1) at (0,-0) {$\tY_{f, n}\Theta\, \underline i$};
    %\node (2) at (0,-1) {$(\lambda z. (\lambda n. \tif{\tsample \underline{- 0.5} < 0}{n}{\tY_{f, n}\Theta\, (n \underline{+ 1})}) z)\, \underline i$};
    \node (3) at (0,-2) {$(\lambda n. \tif{\tsample \underline{- 0.5} < 0}{n}{\tY_{f, n}\Theta\, (n \underline{+ 1})})\, \underline i$};
    \node (4) at (0,-3) {$\tif{\tsample \underline{- 0.5} < 0}{\underline i}{\tY_{f, n}\Theta\, (\underline i\, \underline{+ 1})}$};
    \node (5) at (0,-4) {$\tif{\underline r\, \underline{- 0.5} < 0}{\underline i}{\tY_{f, n}\Theta\, (\underline i\, \underline{+ 1})}$};
    \node (6) at (0,-5) {$\tif{\underline r' < 0}{\underline i}{\tY_{f, n}\Theta\, (\underline i\, \underline{+ 1})}$};
    \node (7) at (2,-6) [text width=] {$\underline i$};
    \node (8) at (0,-7) {$\tY_{f, n}\Theta\, (\underline i\, \underline{+ 1})$};
    \node (9) at (0,-8) {$\tY_{f, n}\Theta\, \underline{i + 1}$};
    %\node (9) at (0,-8) {$(\lambda z. (\lambda n. \tif{\tsample \underline{- 0.5} < 0}{n}{\tY_{f, n}\Theta\, (n \underline{+ 1})}) z)\, (\underline i\, \underline{+ 1})$};
    %\node (10) at (0,-9) {$(\lambda z. (\lambda n. \tif{\tsample \underline{- 0.5} < 0}{n}{\tY_{f, n}\Theta\, (n \underline{+ 1})}) z)\, \underline{i + 1}$};

    \draw [->] (1.south west) to [bend right=45] (3.north west);
    %\draw [->] (2.south west) to [bend right=45] (3.north west);
    \draw [->] (3.south west) to [bend right=45] (4.north west);
    \draw [->] (4.south west) to [bend right=45] (5.north west);
    \draw [->] (5.south west) to [bend right=45] (6.north west);
    \draw [->] (6.south west) to [bend right=45] (8.north west);
    \draw [->] (8.south west) to [bend right=45] (9.north west);
    %\draw [->] (9.south west) to [bend right=45] (10.north west);
    \draw [->] (6) to (7);
\end{tikzpicture}
\caption{Some reachable terms of $\tY_{f, n}\Theta \, \underline 0$\label{fig:geometric distribution 2}}
\end{figure}

\end{example}
